### 2019-12-14 frontmatter.tex
conference/workshop info added

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis summarizes a selection of studies on droplet interactions and suspension flows
        that are relevant to applications in microfluidics, soft matter, and rheology.
        A brief introduction of some basic physical concepts and numerical methods is presented in the first part,
        followed by eight journal articles or preprints listed below. 
        For consistency, the papers have been reformated to fit with the style of the thesis;
        their contents have obviously not been altered.
\end{preface}

@@

	\paperitem
                LB directed the research.
                Z. Ge (ZG) and J-Ch. Loiseau developed, implemented, and validated the methods.
                OT oversaw the entire project.
		ZG wrote the paper with input from the rest of the authors.

	\paperitem
                A. Leshansky (AL) directed the research.
                I. Fouxon (IF) developed the theory.
		ZG performed the simulation.
                IF wrote the paper with input from the rest of the authors.

	\paperitem
                All authors were involved in the discussion of the research.
		ZG developed the idea, performed the simulation,
                and wrote the paper with input from the rest of the authors.

	\paperitem
                AL directed the research.
                IF constructed the theory.
		B. Rubinstein performed the multipole expansion simulation.
                ZG performed the Navier-Stokes simulation.
                IF wrote the paper with input from the rest of the authors.

	\paperitem
                LB conceived the project.
                M.E. Rosti (MER) implemented the method and performed the simulation.
		ZG performed the droplet statistics and scaling analysis.
                S.S. Jain performed the droplet rendering.
                M.S. Dodd performed the turbulent kinetic budget analysis.
                MER wrote the paper with input from the rest of the authors.

	\paperitem
                G. Kreiss initiated the project.
                H. Holmgren implemented the code and performed part of the Stokes simulation.
                M. Kronbichler performed the phase field simulation.
		ZG performed part of the Stokes simulation, and 
                wrote the paper with input from the rest of the authors.

	\paperitem
                M. Minale and LB directed the research.
                R. Martone and C. Carotenuto performed the experiment.
		ZG performed the simulation with help from R. Radhakrishnan,
                and wrote the paper with input from the rest of the authors.

	\paperitem
                LB led the research.
		ZG developed and implemented the method, with input from OT.
                ZG wrote the paper.

@@

%-------------------------------------------------------------------------------
% Conferences (comment if none)
%-------------------------------------------------------------------------------
%
\begin{conferences}
	Part of the work in this thesis has been presented at the following 
	international conferences. The presenting author is underlined.

  \conferenceitem%
    {Anakin Skywalker, \underline{Darth Vader} \& Admiral Motti}% Authors
    {3639}% Year
    {Effects on breathing of underestimation of the power of The Force}% Title
    {Intergalactic Conference on Weapons and Peace}% Conference
    {Kamino}% Location

>>>>

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis summarizes a selection of studies on droplet interactions and suspension flows
        that may find applications in microfluidics, rheology, and soft matter physics.
        A brief introduction of some basic physical concepts and numerical methods is presented in Part I,
        followed by eight journal articles or preprints in Part II, see below.
        For consistency, all papers are formatted in the \texttt{jfm} style as the rest of the thesis.
        Their contents remain faithful to the original publications.
\end{preface}

@@

	\paperitem
                LB directed the research.
                Z. Ge (ZG) and J-Ch. Loiseau developed, implemented, and validated the methods.
                OT oversaw the entire project.
		ZG wrote the paper with inputs from all other authors.

	\paperitem
                A. Leshansky (AL) directed the research.
                I. Fouxon (IF) derived the theory.
		ZG performed the simulation.
                IF wrote the paper with inputs from the rest of the authors.

	\paperitem
                Following Paper 1, ZG continued the research, performed the simulation,
                and wrote the paper with inputs from the rest of the authors.

	\paperitem
                AL directed the research.
                IF constructed the theory.
		B. Rubinstein performed the multipole expansion simulation.
                ZG performed the Navier-Stokes simulation.
                IF wrote the paper with inputs from all other authors.

	\paperitem
                LB conceived the project.
                M.E. Rosti (MER) implemented the method and performed the simulation.
		ZG performed the droplet statistics and scaling analyses.
                S.S. Jain performed the droplet rendering.
                M.S. Dodd performed the turbulent kinetic energy analysis.
                MER wrote the paper with inputs from the rest of the authors.

	\paperitem
                G. Kreiss initiated the project.
                H. Holmgren implemented the code and performed the preliminary Stokes simulation.
                M. Kronbichler performed the phase field simulation.
		ZG performed the final Stokes simulation, and 
                wrote the paper with inputs from the rest of the authors.

	\paperitem
                M. Minale and LB directed the research.
                R. Martone and C. Carotenuto performed the experiment.
                R. Radhakrishnan provided part of the simulation data.
		ZG performed the main simulation and wrote the paper with inputs from the rest of the authors.

	\paperitem
                LB led the research.
		ZG developed and implemented the method, with inputs from OT.
                ZG wrote the paper.

@@

%-------------------------------------------------------------------------------
% Conferences (comment if none)
%-------------------------------------------------------------------------------
%
%\clearpage
\begin{conferences}
        In addition to journal publications, part of the work in this thesis were
        presented in the following conferences and workshops. The presenting author is underlined.

  \conferenceitem%
    {\underline{Z. Ge}, L. Brandt}% Authors
    {2016}% Year
    {Simulation of the self-assembly of colloidal particles in a microchannel}% Title
    {7th Summer school of Complex Motions in Fluids}% Conference
    {Zenderen, Twente, Netherlands}% Location

  \conferenceitem%        
    {Z. Ge, \underline{O. Tammisola}, J.Ch. Loiseau, L. Brandt}% Authors
    {2016}% Year
    {Direct numerical simulation of the self-assembly of colloidal particles in a micro-channel}% Title
    {1$^{st}$ International Conference on Multiscale Applications of Surface Tension}% Conference
    {Brussel, Belgium}% Location

  \conferenceitem%
    {\underline{Z. Ge}, L. Brandt}% Authors
    {2016}% Year
    {Do self-assembly colloidal droplets behave like droplets?}% Title
    {69$^{th}$ Annual Meeting of the APS Division of Fluid Dynamics}% Conference
    {Portland, Oregon, USA}% Location

  \conferenceitem%
    {\underline{Z. Ge}, O. Tammisola, L. Brandt}% Authors
    {2017}% Year
    {A fast mass-preserving interface-correction level set/ghost fluid method for colloidal suspensions under depletion forces}% Title
    {3$^{rd}$ International Conference on Numerical Methods of Multiphase Flows (ICNMMF-III)}% Conference
    {Tokyo, Japan}% Location

  \conferenceitem%
    {\underline{Z. Ge}, H. Holmgren, M. Kronbichler, L. Brandt, G. Kreiss}% Authors
    {2018}% Year
    {Effective slip over partially filled microcavities and its possible failure}% Title
    {12$^{th}$ European Fluid Mechanics Conference}% Conference
    {Vienna, Austria}% Location

  \conferenceitem%
    {\underline{Z. Ge}, O. Tammisola, L. Brandt}% Authors
    {2018}% Year
    {Flow-assisted droplet assembly in a 3D microfluidic channel}% Title
    {71$^{st}$ Annual Meeting of the APS Division of Fluid Dynamics}% Conference
    {Atlanta, Georgia, USA}% Location

  \conferenceitem%
    {\underline{Z. Ge}, O. Tammisola, L. Brandt}% Authors
    {2018}% Year
    {Flow-assisted droplet assembly in a 3D microfluidic channel}% Title
    {Scattering and Dynamics of Flowing Soft Material}% Conference
    {Lund, Sweden}% Location

  \conferenceitem%
    {\underline{Z. Ge}, O. Tammisola, L. Brandt}% Authors
    {2019}% Year
    {Flow-assisted droplet assembly in a 3D microfluidic channel}% Title
    {Colloidal Science \& Metamaterials (CSM)}% Conference
    {Paris, France}% Location
